Summary of Changes in response to Referee's Report

### 2016-01-27 curves-write-up/AIF/changes-summary.tex
changes: minor grammatical edits

\section{Other suggestions}
The referee also made the following notational suggestions,
and here we include reasons we would prefer not to implement them.

\begin{enumerate}
	\item Toward the end of referee comment (1), the referee suggests
		to change the notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
		First, we would like to keep our notation because we often
	list degrees of generation and relations by signatures
	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
	the form $\min(5, e_1, \ldots, e_n)$. These
	seem simpler to
	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
	2s_n + 1)$. Second, because we will be using $e_i$
	so frequently in our analysis, the paper is shortened
	by writing $e_i$ instead of $2s_i+1$.
	Third, we maintained the $e_i$ notation for consistency
	with the notation established in Voight--Zureick-Brown.
	Fourth, since one of our main applications is to modular forms,
	the number theorists reading it may have an easier time translating
	to modular curves whose signature is written with $e_i$ rather than $s_i$.
	\item Prior to referee comment (1), the referee suggests we use orbifold terminology instead
		of stacky terminology. 
		One reason we'd like to keep stacky terminology is
		that the results of this paper hold over a finite field,
		and in the context of finite fields, it seems more natural to work with
		stacks rather than orbifolds.
		Also, since this paper is in many
		ways intimately tied with Voight--Zureick-Brown,
		we would like to keep the use of stacky terminology
		in order to remain compatible with that paper.
	\item Prior to referee comment (1), the referee suggests to remove the signature invariant
		and use the more general terminology from the
		Ice cream paper. We agree that it is
		somewhat difficult to generalize the
		signature terminology,
		and we also note that this signature is commonly used in referring
		to modular curves. Since one of the important
		applications of this paper is to rings of modular
		forms, the signature will play a useful role for
		those interested in the translation to modular curves.
		Once again, we would also like to keep the signature
		to remain compatible with Voight--Zureick-Brown.
\end{enumerate}

>>>>

\section{Other suggestions}
The referee also made the following notational suggestions,
and here we include reasons for why we would prefer not to
implement them.

\begin{enumerate}
	\item Toward the end of referee comment (1), the referee suggests
		to change the notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
		First, we would like to keep our notation because we often
	list degrees of generation and relations by signatures
	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
	the form $\min(5, e_1, \ldots, e_n)$. These
	seem simpler to
	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
	2s_n + 1)$. Second, because we will be using $e_i$
	so frequently in our analysis, the paper is shortened
	by writing $e_i$ instead of $2s_i+1$.
	Third, we maintained the $e_i$ notation for consistency
	with the notation established in Voight--Zureick-Brown.
	Fourth, since one of our main applications is to modular forms,
	number theorists reading the paper may have an easier time
	translating the work to the context of modular curves whose 
	signatures are written with $e_i$ rather than $s_i$.
	\item Prior to referee comment (1), the referee suggests we use 
orbifold terminology instead
		of stacky terminology. 
		One reason we'd like to keep stacky terminology is
		that the results of this paper hold over a finite field,
		and it seems more natural to 
work with	stacks rather than orbifolds in the context of finite fields.
		Also, since this paper is in many
		ways intimately tied with Voight--Zureick-Brown,
		we would like to keep the use of stacky terminology
		in order to remain compatible with that paper.
	\item Prior to referee comment (1), the referee suggests to 
remove the signature invariant
		and use the more general terminology from the
		Ice cream paper. We agree that it is
		somewhat difficult to generalize the
		signature terminology,
		and we also note that this signature is commonly used in 
referring
		to modular curves. Since one of the important
		applications of this paper is to rings of modular
		forms, the signature will play a useful role for
		those interested in the translation to modular curves.
		Once again, we would also like to keep the signature
		to remain compatible with Voight--Zureick-Brown.
\end{enumerate}
